\textbf{Efficient Implementation Strategies for Block Ciphers on ARMv8}\\ {\footnotesize Bachelorarbeit}

### 2023-03-18 Paper/paper.tex
add some code

\lstset{
    basicstyle=\footnotesize\ttfamily,
    breaklines=true
}

\lstset {
    numbers=left,
    stepnumber=1,
    firstnumber=1,
    numberfirstline=true
}

@@

\chapter{Introduction}
\section{Block ciphers}

@@

\begin{lstlisting}[frame=single, caption={Table construction algorithm}, escapechar=|]
    tables <- [][]
    for sbox_index from 0 to 15 do
        for sbox_input from 0 to 15 do|\label{lst:tablesbox}|
            output <- sbox(sbox_input)
            output <- permute(output << (4 * sbox_index))
            tables[sbox_index][sbox_input] <- output
\end{lstlisting}

@@

@@

$n=m=1$ would be a valid choice which yields eight messages divided into four
registers. We choose $n=m=2$ so we can directly utilize the algorithm for bit
packing presented by the original GIFT authors, although it is simple to adapt
this algorithm to only four registers and eight messages by dividing each
128-bit NEON register into two separate 64-bit registers and adjusting the
\texttt{SWAPMOVE} shift and mask values.

@@

@@

@@

We will provide implementations for the presented strategies in the C
programming language. Although directly writing Assembler code could result in
a small performance benefit, this generally increases the work necessary by an
order of magnitude for only limited results.

@@

>>>>

\lstset{
    basicstyle=\scriptsize\ttfamily,
    breaklines=true
}

\lstset {
    frame=single,
    numbers=left,
    stepnumber=1,
    firstnumber=1,
    numberfirstline=true,
    texcl=false
}

@@

\chapter{Introduction}
\section{Notation}

\section{Block ciphers}

@@

\begin{lstlisting}[caption={Table construction algorithm}, escapechar=|]
    tables <- [][]
    for sbox_index from 0 to 15 do
        for sbox_input from 0 to 15 do|\label{lst:tablesbox}|
            output <- sbox(sbox_input)
            output <- permute(output << (4 * sbox_index))
            tables[sbox_index][sbox_input] <- output
\end{lstlisting}

@@

\subsubsection{Parallel S-Boxes}

@@

$n=m=1$ would be a valid choice which yields eight messages divided into four
registers. We choose $n=m=2$ so we can directly utilize the algorithm for bit
packing presented by the original GIFT authors, although it is simple to adapt
this algorithm to only four registers and eight messages by adjusting the
\texttt{SWAPMOVE} shift and mask values.

@@

One caveat of this approach is the fact that NEON registers cannot be shifted
in their entirety due to the fact bits are not able to cross lanes. This leads
to the problem of being able to shift at most two lanes of 64 bits at once. We
thus need to implement the \texttt{shr(V,n)} and \texttt{shl(V,n)} operations
on our own. This can be done by first extracting the 64-bit lanes $a,b$ out of
$V=b||a$, shifting the lanes individually and finally shifting and ORing the
crossing bits back into the other lane.

\begin{alignat*}{2}
    &\text{shl}(V,n): \\
    &\qquad a,b&&=V[0],V[1] \\
    &\qquad c&&=(a\gg (64-n)) \\
    &\qquad a&&=(a\ll n) \\
    &\qquad b&&=(b\ll n)\lor c \\
    &\qquad V[0],V[1]&&=a,b
\end{alignat*}

@@

\subsubsection{Round key function}

In contrast to packing and unpacking of data which is only done once in the
beginning and end, a round key is derived for every round, so the round key
derivation function needs to be as fast as possible. A simple but naive
approach for one round would be to generate a single round key, copy it 15
times and pack the resulting registers similar to how we proceed with the
messages. Due to the cost of packing the messages, this is prohibitivly
expensive. Because we know where each byte group ends up after packing, we can
directly set the round key bits at the correct position. Extending these bits
to bytes can then be done simply by repeatedly shifting and ORing the registers
together.

\subsection{Strategies for Camellia}

@@

We will provide and discuss implementations for the presented strategies in the
C programming language. Although directly writing Assembler code could result
in a small performance benefit, this generally increases the work necessary by
an order of magnitude for only limited results. This is why we use NEON
intrinsics.

\subsection{NEON intrinsics}

The header file \texttt{<arm\_neon.h>} provides ARM-specific data and function
definitions including vector data types and C functions for working with these
vectors. These functions are known as NEON intrinsics and give the programmer a
high-level interface to most NEON instructions. Major advantages of this
approach include the ease of development as the compiler takes over register
allocation and load/store operations as well as performance benefits through
compiler optimizations.

Standard vector data types have the format \texttt{uintnxm\_t} with lane width
$n$ in bits and and lane count $m$. Array types of the format
\texttt{uintnxmxc\_t}, $c\in\{1,2,3,4\}$ are also defined which are used in
operations requiring multiple parameters like \texttt{TBL} or pairwise
load/stores. Intrinsics start with \texttt{v}, optionally contain a \texttt{q}
after the operation name to indicate operation on a 128-bit register and end
with the lane data format. Multiplying eight pairs of 16-bit numbers \texttt{a,b} for
example can be done via the following:

\begin{center}
    \texttt{uint16x8\_t result = vmulq\_u16(a, b);}
\end{center}

The compiler allocates vector registers for \texttt{a}, \texttt{b} and
\texttt{result} and assembles the intrinsic to \texttt{MUL Vr.8H, Va.8H,
Vb.8H}. Necessary load and stores for the result and parameters are also
handled automatically.

@@

\chapter{Appendix}

\begin{lstlisting}[language=c, caption={gift\_vec\_sliced.h}]
#ifndef GIFT_VEC_SLICED_H
#define GIFT_VEC_SLICED_H

#include <stdint.h>
#include <arm_neon.h>

#define ROUNDS_GIFT_64 28

// expose for benchmarking
uint8x16_t shl(uint8x16_t v, int n);
uint8x16_t shr(uint8x16_t v, int n);
void gift_64_vec_sliced_swapmove(uint8x16_t *restrict a, uint8x16_t *restrict b,
                                 uint8x16_t m, int n);
void gift_64_vec_sliced_bits_pack(uint8x16x4_t m[restrict 2]);

void gift_64_vec_sliced_subcells(uint8x16x4_t cipher_state[restrict 2]);
void gift_64_vec_sliced_subcells_inv(uint8x16x4_t cipher_state[restrict 2]);
void gift_64_vec_sliced_permute(uint8x16x4_t cipher_state[restrict 2]);
void gift_64_vec_sliced_permute_inv(uint8x16x4_t cipher_state[2]);
void gift_64_vec_sliced_generate_round_keys(uint8x16x4_t round_keys[restrict ROUNDS_GIFT_64][2],
                                            const uint64_t key[restrict 2]);

void gift_64_vec_sliced_init(void);

void gift_64_vec_sliced_encrypt(uint64_t c[restrict 16],
                                const uint64_t m[restrict 16],
                                const uint64_t key[restrict 2]);
void gift_64_vec_sliced_decrypt(uint64_t m[restrict 16],
                                const uint64_t c[restrict 16],
                                const uint64_t key[restrict 2]);

#endif
\end{lstlisting}

\begin{lstlisting}[language=c, caption={gift\_vec\_sliced.c}]
#include "gift_vec_sliced.h"

#include <stddef.h>
#include <stdio.h>
#include <string.h>

static uint64_t perm_u64[16] = {
        0x1410050115110400UL, 0x1410050115110400UL,
        0x0501151104001410UL, 0x0501151104001410UL,
        0x1511040014100501UL, 0x1511040014100501UL,
        0x0400141005011511UL, 0x0400141005011511UL,
        0x1612070317130602UL, 0x1612070317130602UL,
        0x0703171306021612UL, 0x0703171306021612UL,
        0x1713060216120703UL, 0x1713060216120703UL,
        0x0602161207031713UL, 0x0602161207031713UL
};

static uint64_t perm_inv_u64[16] = {
        0x1511050114100400UL, 0x1511050114100400UL,
        0x1713070316120602UL, 0x1713070316120602UL,
        0x1115010510140004UL, 0x1115010510140004UL,
        0x1317030712160206UL, 0x1317030712160206UL,
        0x1317030712160206UL, 0x1317030712160206UL,
        0x1511050114100400UL, 0x1511050114100400UL,
        0x1713070316120602UL, 0x1713070316120602UL,
        0x1115010510140004UL, 0x1115010510140004UL
};

static uint8x16x4_t perm[2];
static uint8x16x4_t perm_inv[2];

static uint8x16_t pack_mask_0;
static uint8x16_t pack_mask_1;
static uint8x16_t pack_mask_2;

static const int round_constant[] = {
        // rounds 0-15
        0x01, 0x03, 0x07, 0x0F, 0x1F, 0x3E, 0x3D, 0x3B,
        0x37, 0x2F, 0x1E, 0x3C, 0x39, 0x33, 0x27, 0x0E,
        // rounds 16-31
        0x1D, 0x3A, 0x35, 0x2B, 0x16, 0x2C, 0x18, 0x30,
        0x21, 0x02, 0x05, 0x0B, 0x17, 0x2E, 0x1C, 0x38,
        // rounds 32-47
        0x31, 0x23, 0x06, 0x0D, 0x1B, 0x36, 0x2D, 0x1A,
        0x34, 0x29, 0x12, 0x24, 0x08, 0x11, 0x22, 0x04
};

uint8x16_t shl(uint8x16_t v, int n)
{
        // TODO check out vst
        uint64_t l0 = vgetq_lane_u64(v, 0);
        uint64_t l1 = vgetq_lane_u64(v, 1);
        l1 = l1 << n | (l0 >> (64 - n));
        l0 <<= n;
        uint8x16_t ret;
        ret = vsetq_lane_u64(l0, ret, 0);
        ret = vsetq_lane_u64(l1, ret, 1);
        return ret;
}

uint8x16_t shr(uint8x16_t v, int n)
{
        uint64_t l0 = vgetq_lane_u64(v, 0);
        uint64_t l1 = vgetq_lane_u64(v, 1);
        l0 = l0 >> n | (((l1 << (64 - n)) >> (64 - n)) << (64 - n));
        l1 >>= n;
        uint8x16_t ret;
        ret = vsetq_lane_u64(l0, ret, 0);
        ret = vsetq_lane_u64(l1, ret, 1);
        return ret;
}

void gift_64_vec_sliced_swapmove(uint8x16_t *restrict a, uint8x16_t *restrict b, uint8x16_t m, int n)
{

        uint8x16_t t = vandq_u8(veorq_u8(shr(*a, n), *b), m);
        *b = veorq_u8(*b, t);
        *a = veorq_u8(*a, shl(t, n));
}

void gift_64_vec_sliced_bits_pack(uint8x16x4_t m[restrict 2])
{
        // take care not to shift mask bits out of the register
        gift_64_vec_sliced_swapmove(&m[0].val[0], &m[0].val[1], pack_mask_0, 1);
        gift_64_vec_sliced_swapmove(&m[0].val[2], &m[0].val[3], pack_mask_0, 1);
        gift_64_vec_sliced_swapmove(&m[1].val[0], &m[1].val[1], pack_mask_0, 1);
        gift_64_vec_sliced_swapmove(&m[1].val[2], &m[1].val[3], pack_mask_0, 1);

        gift_64_vec_sliced_swapmove(&m[0].val[0], &m[0].val[2], pack_mask_1, 2);
        gift_64_vec_sliced_swapmove(&m[0].val[1], &m[0].val[3], pack_mask_1, 2);
        gift_64_vec_sliced_swapmove(&m[1].val[0], &m[1].val[2], pack_mask_1, 2);
        gift_64_vec_sliced_swapmove(&m[1].val[1], &m[1].val[3], pack_mask_1, 2);

        // make bytes (a0 b0 c0 d0 a4 b4 c4 d4 -> a0 b0 c0 d0 e0 f0 g0 h0)
        gift_64_vec_sliced_swapmove(&m[0].val[0], &m[1].val[0], pack_mask_2, 4);
        gift_64_vec_sliced_swapmove(&m[0].val[2], &m[1].val[2], pack_mask_2, 4);
        gift_64_vec_sliced_swapmove(&m[0].val[1], &m[1].val[1], pack_mask_2, 4);
        gift_64_vec_sliced_swapmove(&m[0].val[3], &m[1].val[3], pack_mask_2, 4);
}

void gift_64_vec_sliced_subcells(uint8x16x4_t cs[restrict 2])
{
        cs[0].val[1] = veorq_u8(cs[0].val[1], vandq_u8(cs[0].val[0], cs[0].val[2]));
        uint8x16_t t = veorq_u8(cs[0].val[0], vandq_u8(cs[0].val[1], cs[0].val[3]));
        cs[0].val[2] = veorq_u8(cs[0].val[2], vorrq_u8(t, cs[0].val[1]));
        cs[0].val[0] = veorq_u8(cs[0].val[3], cs[0].val[2]);
        cs[0].val[1] = veorq_u8(cs[0].val[1], cs[0].val[0]);
        cs[0].val[0] = vmvnq_u8(cs[0].val[0]);
        cs[0].val[2] = veorq_u8(cs[0].val[2], vandq_u8(t, cs[0].val[1]));
        cs[0].val[3] = t;

        cs[1].val[1] = veorq_u8(cs[1].val[1], vandq_u8(cs[1].val[0], cs[1].val[2]));
        t            = veorq_u8(cs[1].val[0], vandq_u8(cs[1].val[1], cs[1].val[3]));
        cs[1].val[2] = veorq_u8(cs[1].val[2], vorrq_u8(t, cs[1].val[1]));
        cs[1].val[0] = veorq_u8(cs[1].val[3], cs[1].val[2]);
        cs[1].val[1] = veorq_u8(cs[1].val[1], cs[1].val[0]);
        cs[1].val[0] = vmvnq_u8(cs[1].val[0]);
        cs[1].val[2] = veorq_u8(cs[1].val[2], vandq_u8(t, cs[1].val[1]));
        cs[1].val[3] = t;
}

void gift_64_vec_sliced_subcells_inv(uint8x16x4_t cs[restrict 2])
{
        uint8x16_t t = cs[0].val[3];
        cs[0].val[2] = veorq_u8(cs[0].val[2], vandq_u8(t, cs[0].val[1]));
        cs[0].val[0] = vmvnq_u8(cs[0].val[0]);
        cs[0].val[1] = veorq_u8(cs[0].val[1], cs[0].val[0]);
        cs[0].val[3] = veorq_u8(cs[0].val[0], cs[0].val[2]);
        cs[0].val[2] = veorq_u8(cs[0].val[2], vorrq_u8(t, cs[0].val[1]));
        cs[0].val[0] = veorq_u8(t, vandq_u8(cs[0].val[1], cs[0].val[3]));
        cs[0].val[1] = veorq_u8(cs[0].val[1], vandq_u8(cs[0].val[0], cs[0].val[2]));

        t            = cs[1].val[3];
        cs[1].val[2] = veorq_u8(cs[1].val[2], vandq_u8(t, cs[1].val[1]));
        cs[1].val[0] = vmvnq_u8(cs[1].val[0]);
        cs[1].val[1] = veorq_u8(cs[1].val[1], cs[1].val[0]);
        cs[1].val[3] = veorq_u8(cs[1].val[0], cs[1].val[2]);
        cs[1].val[2] = veorq_u8(cs[1].val[2], vorrq_u8(t, cs[1].val[1]));
        cs[1].val[0] = veorq_u8(t, vandq_u8(cs[1].val[1], cs[1].val[3]));
        cs[1].val[1] = veorq_u8(cs[1].val[1], vandq_u8(cs[1].val[0], cs[1].val[2]));
}

void gift_64_vec_sliced_permute(uint8x16x4_t cs[restrict 2])
{
        uint8x16x2_t pairs[4] = {
                { .val = { cs[0].val[0], cs[1].val[0] }},
                { .val = { cs[0].val[1], cs[1].val[1] }},
                { .val = { cs[0].val[2], cs[1].val[2] }},
                { .val = { cs[0].val[3], cs[1].val[3] }},
        };

        cs[0].val[0] = vqtbl2q_u8(pairs[0], perm[0].val[0]);
        cs[0].val[1] = vqtbl2q_u8(pairs[1], perm[0].val[1]);
        cs[0].val[2] = vqtbl2q_u8(pairs[2], perm[0].val[2]);
        cs[0].val[3] = vqtbl2q_u8(pairs[3], perm[0].val[3]);

        cs[1].val[0] = vqtbl2q_u8(pairs[0], perm[1].val[0]);
        cs[1].val[1] = vqtbl2q_u8(pairs[1], perm[1].val[1]);
        cs[1].val[2] = vqtbl2q_u8(pairs[2], perm[1].val[2]);
        cs[1].val[3] = vqtbl2q_u8(pairs[3], perm[1].val[3]);
}

void gift_64_vec_sliced_permute_inv(uint8x16x4_t cs[restrict 2])
{
        uint8x16x2_t pairs[4] = {
                { .val = { cs[0].val[0], cs[1].val[0] }},
                { .val = { cs[0].val[1], cs[1].val[1] }},
                { .val = { cs[0].val[2], cs[1].val[2] }},
                { .val = { cs[0].val[3], cs[1].val[3] }},
        };

        cs[0].val[0] = vqtbl2q_u8(pairs[0], perm_inv[0].val[0]);
        cs[0].val[1] = vqtbl2q_u8(pairs[1], perm_inv[0].val[1]);
        cs[0].val[2] = vqtbl2q_u8(pairs[2], perm_inv[0].val[2]);
        cs[0].val[3] = vqtbl2q_u8(pairs[3], perm_inv[0].val[3]);

        cs[1].val[0] = vqtbl2q_u8(pairs[0], perm_inv[1].val[0]);
        cs[1].val[1] = vqtbl2q_u8(pairs[1], perm_inv[1].val[1]);
        cs[1].val[2] = vqtbl2q_u8(pairs[2], perm_inv[1].val[2]);
        cs[1].val[3] = vqtbl2q_u8(pairs[3], perm_inv[1].val[3]);
}

void gift_64_vec_sliced_generate_round_keys(uint8x16x4_t round_keys[restrict ROUNDS_GIFT_64][2],
                                            const uint64_t key[restrict 2])
{
        // TODO shift-and-or

        uint64_t key_state[] = {key[0], key[1]};
        for (int round = 0; round < ROUNDS_GIFT_64; round++) {
                int v = (key_state[0] >> 0 ) & 0xffff;
                int u = (key_state[0] >> 16) & 0xffff;

                // add round key (RK=U||V)
                uint64_t round_key[8] = { 0x0UL };
                for (size_t i = 0; i < 8; i++) {
                        int key_bit_v   = (v >> (2 * i + 0)) & 0x1;
                        int key_bit_u   = (u >> (2 * i + 0)) & 0x1;
                        round_key[0] ^= (uint64_t)key_bit_v << (i * 8);
                        round_key[1] ^= (uint64_t)key_bit_u << (i * 8);

                        key_bit_v   = (v >> (2 * i + 1)) & 0x1;
                        key_bit_u   = (u >> (2 * i + 1)) & 0x1;
                        round_key[4] ^= (uint64_t)key_bit_v << (i * 8);
                        round_key[5] ^= (uint64_t)key_bit_u << (i * 8);
                }

                // add single bit
                round_key[7] ^= 1UL << (7 * 8);

                // add round constants
                round_key[3] ^= ((round_constant[round] >> 0) & 0x1) << (0 * 8);
                round_key[7] ^= ((round_constant[round] >> 1) & 0x1) << (0 * 8);
                round_key[3] ^= ((round_constant[round] >> 2) & 0x1) << (1 * 8);
                round_key[7] ^= ((round_constant[round] >> 3) & 0x1) << (1 * 8);
                round_key[3] ^= ((round_constant[round] >> 4) & 0x1) << (2 * 8);
                round_key[7] ^= ((round_constant[round] >> 5) & 0x1) << (2 * 8);

                // extend bits to bytes
                for (size_t i = 0; i < 8; i++) {
                        round_key[i] |= round_key[i] << 1;
                        round_key[i] |= round_key[i] << 2;
                        round_key[i] |= round_key[i] << 4;
                }

                // load into vector registers (upper and lower part are same)
                round_keys[round][0].val[0] = vdupq_n_u64(round_key[0]);
                round_keys[round][0].val[1] = vdupq_n_u64(round_key[1]);
                round_keys[round][0].val[2] = vdupq_n_u64(round_key[2]);
                round_keys[round][0].val[3] = vdupq_n_u64(round_key[3]);
                round_keys[round][1].val[0] = vdupq_n_u64(round_key[4]);
                round_keys[round][1].val[1] = vdupq_n_u64(round_key[5]);
                round_keys[round][1].val[2] = vdupq_n_u64(round_key[6]);
                round_keys[round][1].val[3] = vdupq_n_u64(round_key[7]);

                // update key state
                int k0 = (key_state[0] >> 0 ) & 0xffffUL;
                int k1 = (key_state[0] >> 16) & 0xffffUL;
                k0 = (k0 >> 12) | ((k0 & 0xfff) << 4);
                k1 = (k1 >> 2 ) | ((k1 & 0x3  ) << 14);
                key_state[0] >>= 32;
                key_state[0] |= (key_state[1] & 0xffffffffUL) << 32;
                key_state[1] >>= 32;
                key_state[1] |= ((uint64_t)k0 << 32) | ((uint64_t)k1 << 48);
        }
}

void gift_64_vec_sliced_init(void)
{
        // permutations
        perm[0] = vld1q_u8_x4((uint8_t*)&perm_u64[0]);
        perm[1] = vld1q_u8_x4((uint8_t*)&perm_u64[8]);

        // inverse permutations
        perm_inv[0] = vld1q_u8_x4((uint8_t*)&perm_inv_u64[0]);
        perm_inv[1] = vld1q_u8_x4((uint8_t*)&perm_inv_u64[8]);

        // packing masks
        pack_mask_0 = vdupq_n_u8(0x55);
        pack_mask_1 = vdupq_n_u8(0x33);
        pack_mask_2 = vdupq_n_u8(0x0f);
}

void gift_64_vec_sliced_encrypt(uint64_t c[restrict 16],
                                const uint64_t m[restrict 16],
                                const uint64_t key[restrict 2])
{
        uint8x16x4_t s[2];
        s[0] = vld1q_u8_x4((uint8_t*)&m[0]);
        s[1] = vld1q_u8_x4((uint8_t*)&m[8]);
        gift_64_vec_sliced_bits_pack(s);

        uint8x16x4_t round_keys[ROUNDS_GIFT_64][2];
        gift_64_vec_sliced_generate_round_keys(round_keys, key);

        for (int round = 0; round < ROUNDS_GIFT_64; round++) {
                gift_64_vec_sliced_subcells(s);
                gift_64_vec_sliced_permute(s);

                s[0].val[0] = veorq_u8(s[0].val[0], round_keys[round][0].val[0]);
                s[0].val[1] = veorq_u8(s[0].val[1], round_keys[round][0].val[1]);
                s[0].val[2] = veorq_u8(s[0].val[2], round_keys[round][0].val[2]);
                s[0].val[3] = veorq_u8(s[0].val[3], round_keys[round][0].val[3]);
                s[1].val[0] = veorq_u8(s[1].val[0], round_keys[round][1].val[0]);
                s[1].val[1] = veorq_u8(s[1].val[1], round_keys[round][1].val[1]);
                s[1].val[2] = veorq_u8(s[1].val[2], round_keys[round][1].val[2]);
                s[1].val[3] = veorq_u8(s[1].val[3], round_keys[round][1].val[3]);
        }

        gift_64_vec_sliced_bits_pack(s);
        vst1q_u8_x4((uint8_t*)&c[0], s[0]);
        vst1q_u8_x4((uint8_t*)&c[8], s[1]);
}

void gift_64_vec_sliced_decrypt(uint64_t m[restrict 16],
                                const uint64_t c[restrict 16],
                                const uint64_t key[restrict 2])
{
        uint8x16x4_t s[2];
        s[0] = vld1q_u8_x4((uint8_t*)&c[0]);
        s[1] = vld1q_u8_x4((uint8_t*)&c[8]);
        gift_64_vec_sliced_bits_pack(s);

        uint8x16x4_t round_keys[ROUNDS_GIFT_64][2];
        gift_64_vec_sliced_generate_round_keys(round_keys, key);

        for (int round = ROUNDS_GIFT_64 - 1; round >= 0; round--) {
                s[0].val[0] = veorq_u8(s[0].val[0], round_keys[round][0].val[0]);
                s[0].val[1] = veorq_u8(s[0].val[1], round_keys[round][0].val[1]);
                s[0].val[2] = veorq_u8(s[0].val[2], round_keys[round][0].val[2]);
                s[0].val[3] = veorq_u8(s[0].val[3], round_keys[round][0].val[3]);
                s[1].val[0] = veorq_u8(s[1].val[0], round_keys[round][1].val[0]);
                s[1].val[1] = veorq_u8(s[1].val[1], round_keys[round][1].val[1]);
                s[1].val[2] = veorq_u8(s[1].val[2], round_keys[round][1].val[2]);
                s[1].val[3] = veorq_u8(s[1].val[3], round_keys[round][1].val[3]);

                gift_64_vec_sliced_permute_inv(s);
                gift_64_vec_sliced_subcells_inv(s);
        }

        gift_64_vec_sliced_bits_pack(s);
        vst1q_u8_x4((uint8_t*)&m[0], s[0]);
        vst1q_u8_x4((uint8_t*)&m[8], s[1]);
}
\end{lstlisting}
